Draft_Mid_Term

### 2022-10-05 Draft_Mid_Term.Rmd
regression

palette5 <- c("#0571b0","#92c5de","#ffffbf","#f4a582","#ca0020")
```

```{r set_directory,include=FALSE}
setwd("C:/Users/yyp/Desktop/Upenn/MUSA/courses/MUSA5080/Midterm")
```

@@

### 2.1.1 Data loading
```{r raw_data}
#Raw Data:
data<-st_read("./data/studentData.geojson")

@@

#Census Tract:
tract<-st_read('./data/CensusTract/Census_Tracts_2020.shp')
tract<-tract %>% st_transform(crs=4326)

#Zipcode:
##用于neighborhood effects分析
zipcode<-st_read('./data/zipcode/Zipcode.shp')
zipcode<-zipcode %>% st_transform(crs=4326) %>% rename(shapeLeng = shape_Leng,shapeArea = shape_Area) %>% dplyr::select(zip,po_name,shapeLeng,shapeArea)
```

```{r}
ggplot()+
  geom_sf(data=st_union(zipcode))+
  geom_sf(data=park_amenities.sf)
```

```{r}
ggplot()+
  geom_sf(data=st_union(tract))+
  geom_sf(data=park_easement.sf)
```

@@

#10.Capital Improvement Projects:
capital_improve<-st_read('./data/Capital_Improvement_Projects/Capital_Improvement_Projects.shp')
capital_improve.sf<-capital_improve %>% st_transform(crs=4326)%>% dplyr::select(geometry) %>% na.omit()

#11.Business Investment Opportunity Zones:
##这个=做binary指标。原始数据是polygon;考虑使用buffer?
business_invest<-st_read('./data/Business/Business_Investment_Opportunity_Zones.shp')
business_invest<-business_invest %>% st_transform(crs=4326)
```

@@

#4.Percent of canopy in residential area:
canopy<-st_read('./data/Tree Canopy - Residential.geojson')
Pctcanopy<-canopy %>% st_transform(crs=4326) %>% mutate(Pctcanopy = X2012) %>% dplyr::select(Pctcanopy)

#5.Percent of Test Proficiency in Elementary Schools:
test_elementary<-st_read('./data/Test Proficiency - Elementary School.geojson')
Pcttest1<-test_elementary%>% st_transform(crs=4326) %>%mutate( test.elementary = X2019) %>% dplyr::select(test.elementary)

#6.Percent of Test Proficiency in Middle Schools:
test_middle<-st_read('./data/Test Proficiency - Middle School.geojson')
Pcttest2<-test_middle%>% st_transform(crs=4326) %>%mutate( test.middle = X2019) %>% dplyr::select(test.middle)

#7.Percent of Test Proficiency in High Schools:
test_high<-st_read('./data/Test Proficiency - High School.geojson')
Pcttest3<-test_high%>% st_transform(crs=4326) %>% mutate(test.high = X2019) %>% dplyr::select(test.high)

#8.Percent of Bachelor's Degree:
bachelor<-st_read('./data/Education Level - Bachelor Degree.geojson')
PctBachelor<-bachelor %>% st_transform(crs=4326) %>% mutate(PctBachelor = X2020) %>% dplyr::select(PctBachelor)

#9.Median Age of Residents:
age<-st_read('./data/Age of Residents.geojson')
MedAge<-age %>% st_transform(crs=4326) %>% mutate(MedAge = X2020) %>% dplyr::select(MedAge)
```

@@

```{r data_left_join}
data<-st_join(data,crime1)
data<-st_join(data,long_commute)
data<-st_join(data,Pctgrocery)
data<-st_join(data,Pctcanopy)
data<-st_join(data,Pcttest1)
data<-st_join(data,Pcttest2)
data<-st_join(data,Pcttest3)
data<-st_join(data,PctBachelor)
data<-st_join(data,MedAge)
data<-st_join(data,zipcode)
data<-st_join(data,tracts20)
```

@@

#9.park easement:
data <-
  data %>% 
  mutate(
    park_easement_nn1 = nn_function(st_c(data),st_c(park_easement.sf), 1),
    park_easement_nn2 = nn_function(st_c(data),st_c(park_easement.sf), 2),
    park_easement_nn3 = nn_function(st_c(data),st_c(park_easement.sf), 3),
    park_easement_nn4 = nn_function(st_c(data),st_c(park_easement.sf), 4),
    park_easement_nn5 = nn_function(st_c(data),st_c(park_easement.sf), 5),
    )

@@

```{r eval=FALSE}
#8.park_amenities:
###这个需要将三围点变成二维点
data0 <-
  data0 %>% 
  mutate(
    park_amenities_nn1 = nn_function(st_c(data0),st_c(park_amenities.sf), 1),
    park_amenities_nn2 = nn_function(st_c(data0),st_c(park_amenities.sf), 2),
    park_amenities_nn3 = nn_function(st_c(data0),st_c(park_amenities.sf), 3),
    park_amenities_nn4 = nn_function(st_c(data0),st_c(park_amenities.sf), 4),
    park_amenities_nn5 = nn_function(st_c(data0),st_c(park_amenities.sf), 5),
    )
```

@@

```{r model_set}
#model_set:建模组,crs=4326
model_set<-data %>% filter(price!=0)
```

## 2.2 Summary Statistics of Features

model_set internal features
```{r summary_internal_features}
#Summary and selection of internal features:
internal.features<-model_set%>% dplyr::select(price,shape_Area,pricepersq,AGE,heatedarea,numfirepla,fullbaths,halfbaths,bedrooms,units) %>% st_drop_geometry()

@@

ggcorrplot(
  round(cor(numericVars), 1), 
  p.mat = cor_pmat(numericVars),
  colors = c("#0571b0", "#ffffff", "#ca0020"),
  type="lower",
  insig = "pch") +  
    labs(title = "Correlation across numeric variables")+plotTheme()
```
```{r summary_amenities_feature}
amenities_feature.list<-data %>% dplyr::select(starts_with('daycare_'),starts_with('MedicalFacilities_'),starts_with('hist_c'),starts_with('park_'),starts_with('capital_'),starts_with('Pct'),starts_with('test.e'),pctTotalVacant, pctRenterOccupied, pctWhite,pctPoverty,MedRent ,MedHHInc,MedAge) %>% st_drop_geometry()

#stargazer:
stargazer(amenities_feature.list, type = "html", 
          title = "Table DATA 2.1 Summary Statistics of Internal Characteristics ",
          header = FALSE,
          single.row = TRUE)
```

```{r amenities_feature_matrix}
numericVars2 <- 
  select_if(amenities_feature.list, is.numeric) %>% na.omit()

ggcorrplot(
  round(cor(numericVars2), 1), 
  p.mat = cor_pmat(numericVars2),
  colors = c("#0571b0", "#ffffff", "#ca0020"),
  type="lower",
  insig = "pch") +  
    labs(title = "Correlation across numeric variables")+plotTheme()
```

>>>>

palette5 <- c("#0571b0","#92c5de","#ffffbf","#f4a582","#ca0020")

setwd("~/Github/508_houseprice_prediction")
```

@@

### 2.1.1 Data loading
```{r raw_data}
#Raw Data:
data<-st_read("~/Github/508_houseprice_prediction/data/studentData.geojson")

@@

#Census Tract:
tract<-st_read('~/Github/508_houseprice_prediction/data/CensusTract/Census_Tracts_2020.shp')
tract<-tract %>% st_transform(crs=4326)

#Zipcode:
##用于neighborhood effects分析
zipcode<-st_read('~/Github/508_houseprice_prediction/data/zipcode/Zipcode.shp')
zipcode<-zipcode %>% st_transform(crs=4326) %>% rename(shapeLeng = shape_Leng,shapeArea = shape_Area) %>% dplyr::select(zip,po_name,shapeLeng,shapeArea)
```

@@

#10.park location:
park_location <- st_read('./data/Park_Locations/Park_Locations.shp')
park_location.sf <- park_location %>% st_transform(crs=4326)%>%st_centroid() %>% dplyr::select(geometry) %>% na.omit()

#11.Capital Improvement Projects:
capital_improve<-st_read('./data/Capital_Improvement_Projects/Capital_Improvement_Projects.shp')
capital_improve.sf<-capital_improve %>% st_transform(crs=4326)%>% dplyr::select(geometry) %>% na.omit()

#12.Business Investment Opportunity Zones:
##这个=做binary指标。原始数据是polygon;考虑使用buffer?
business_invest<-st_read('./data/Business/Business_Investment_Opportunity_Zones.shp')
business_invest<-business_invest %>% st_transform(crs=4326)
```

```{r}
ggplot()+
  geom_sf(data=st_union(zipcode))+
  geom_sf(data=park_amenities.sf)
```
```{r}
ggplot()+
  geom_sf(data=st_union(tract))+
  geom_sf(data=park_easement.sf)
```

@@

#4.Percent of Test Proficiency in Elementary Schools:
test_elementary<-st_read('./data/Test Proficiency - Elementary School.geojson')
Pcttest1<-test_elementary%>% st_transform(crs=4326) %>%mutate( test.elementary = X2019) %>% dplyr::select(test.elementary)

#5.Percent of Test Proficiency in Middle Schools:
test_middle<-st_read('./data/Test Proficiency - Middle School.geojson')
Pcttest2<-test_middle%>% st_transform(crs=4326) %>%mutate( test.middle = X2019) %>% dplyr::select(test.middle)

#6.Percent of Test Proficiency in High Schools:
test_high<-st_read('./data/Test Proficiency - High School.geojson')
Pcttest3<-test_high%>% st_transform(crs=4326) %>% mutate(test.high = X2019) %>% dplyr::select(test.high)

#7.Percent of Bachelor's Degree:
bachelor<-st_read('./data/Education Level - Bachelor Degree.geojson')
PctBachelor<-bachelor %>% st_transform(crs=4326) %>% mutate(PctBachelor = X2020) %>% dplyr::select(PctBachelor)

#8.Median Age of Residents:
age<-st_read('./data/Age of Residents.geojson')
MedAge<-age %>% st_transform(crs=4326) %>% mutate(MedAge = X2020) %>% dplyr::select(MedAge)
```

@@

```{r data_left_join}
data<-st_join(data,crime1)
data<-st_join(data,long_commute)
data<-st_join(data,Pctgrocery)
data<-st_join(data,Pcttest1)
data<-st_join(data,Pcttest2)
data<-st_join(data,Pcttest3)
data<-st_join(data,PctBachelor)
data<-st_join(data,MedAge)
data<-st_join(data,zipcode)
data<-st_join(data,tracts20)
```

@@

#9.park easement:
data <-
  data %>% 
  mutate(
    park_location_nn1 = nn_function(st_c(data),st_c(park_location.sf), 1),
    park_location_nn2 = nn_function(st_c(data),st_c(park_location.sf), 2),
    park_location_nn3 = nn_function(st_c(data),st_c(park_location.sf), 3),
    park_location_nn4 = nn_function(st_c(data),st_c(park_location.sf), 4),
    park_location_nn5 = nn_function(st_c(data),st_c(park_location.sf), 5),
    )

@@

@@

```{r model_set}
#model_set:建模组,crs=4326
model_set<-data %>% filter(price!=0)
```
## 2.2 Summary Statistics of Features

model_set internal features
```{r summary_internal_features}
#Summary and selection of internal features:
internal.variable <- c("price",
                "shape_Area",
                "pricepersq",
                "AGE",
                "heatedarea",
                "numfirepla",
                "fullbaths",
                "halfbaths",
                "bedrooms",
                "units")

internal.features<-model_set[internal.variable] %>%
  st_drop_geometry()

@@

ggcorrplot(
  round(cor(numericVars), 1), 
  p.mat = cor_pmat(numericVars),
  colors = c("#0571b0", "#ffffff", "#ca0020"),
  type="lower",
  insig = "pch") +  
    labs(title = "Correlation across numeric variables\n(internal features)\n")+plotTheme()
```
remove AGE, units is a good feature do not have strong correlation with other features and have strong corelation with price.
```{r}
sel.internal.list <-  c("price",
                "shape_Area",
                "pricepersq",
                "heatedarea",
                "numfirepla",
                "fullbaths",
                "halfbaths",
                "bedrooms",
                "units")
```

```{r summary_amenities_feature}
amenities_feature.list<-data %>% dplyr::select(
  starts_with('college_'),
  starts_with('daycare_'),
  starts_with('MedicalFacilities_'),
  starts_with('library_'),
  starts_with('hist_'),
  starts_with('church'),
  starts_with('park_'),
  starts_with('capital_'),
  price) %>% 
  st_drop_geometry()

#stargazer:
stargazer(amenities_feature.list, type = "html", 
          title = "Table DATA 2.1 Summary Statistics of Internal Characteristics ",
          header = FALSE,
          single.row = TRUE)
```
```{r amenities_feature_matrix}
ggcorrplot(
  round(cor(amenities_feature.list), 1), 
  p.mat = cor_pmat(amenities_feature.list),
  colors = c("#0571b0", "#ffffff", "#ca0020"),
  type="lower",
  insig = "pch") +  
  labs(title = "Correlation across numeric variables\n(amenity features)\n")+plotTheme()+
  theme(axis.title.x = element_text(size=3),axis.title.y = element_text(size=3))
```

```{r}
sel.amenitie<-data %>% dplyr::select(
  starts_with('college_'),
  starts_with('daycare_'),
  starts_with('MedicalFacilities_'),
  starts_with('library_'),
  starts_with('hist_'),
  starts_with('church'),
  starts_with('capital_'),
  price) %>% 
  st_drop_geometry()
```

```{r}
tract.list <- c("pctTotalVacant", "pctRenterOccupied", "pctWhite","pctPoverty","MedRent" ,"MedHHInc","MedAge","crime_sum", "PctLongCommute", "Pctgrocery", "test.elementary","test.middle", "test.high","PctBachelor","MedAge",'price')

tract_feature.list<-data[tract.list]%>% 
  st_drop_geometry()

```

```{r amenities_feature_matrix}
numeric.tract<- 
  select_if(tract_feature.list, is.numeric) %>% na.omit()

ggcorrplot(
  round(cor(numeric.tract), 1), 
  p.mat = cor_pmat(numeric.tract),
  colors = c("#0571b0", "#ffffff", "#ca0020"),
  type="lower",
  insig = "pch") +  
  labs(title = "Correlation across numeric variables\n public service features\n")+plotTheme()+
  theme(axis.title.x = element_text(size=3),axis.title.y = element_text(size=3))

sel.tract.list<- c( "pctRenterOccupied", "pctWhite","pctPoverty","MedRent" ,"MedHHInc","MedAge","crime_sum", "PctLongCommute", "Pctgrocery",  "test.high","PctBachelor","MedAge",'price')
```
## 2.3 Regression for Feature Selection
### 2.3.1 non numeric Feature Selection

```{r}
numeric<- select_if(data, is.numeric)%>% na.omit()%>% 
  st_drop_geometry()
```
!(data %in% c(value1, value2, value3, ...))

```{r}
nonnumeric <- select_if(data, !(colnames(data)%in% colnames(numeric)))
```

```{r}
names(nonnumeric)
```
```{r}
a = ls()
rm(list=a[which(a!='data' & a !='sel.internal.list' & a !='sel.tract.list' & a !='sel.amenitie')])
```

```{r}

nonnumeric.feature1 <- c("descbuildi", "storyheigh", "aheatingty", "heatedfuel", "extwall", "foundation", "bldggrade","price")

nonnumeric <- data[nonnumeric.feature]%>% 
  st_drop_geometry()

```
"stname", "sttype",  "city", "state",

```{r}
M1 <- lm(price ~ ., data = nonnumeric)

```

```{r}
M2 <- lm(price ~ ., data = data[sel.internal.list])
```

```{r}
M3 <- lm(price ~ ., data = data[sel.tract.list])
```

```{r}
M4 <- lm(price ~., data = sel.amenitie)
```
